### 2016-05-19 2016-lrec-tyvmorph/poster.tex
a few updates and changes
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@68640 72bbbca6-d526-0410-a7d9-f06f51895060

	\headerbox{Tuvan}{name=tyvan,column=0,row=0}{
		\includegraphics[width=\textwidth]{img/tuvanmap}
		\tikzoverlay[text width=1in] at (2.5in, -0in) {
			\includegraphics[width=1in]{img/Flag_of_Tuva}
		};
		\vspace{-1.2em}
		\begin{itemize}
			\item Sayan Turkic language
			\item Spoken in the Tuva Republic
			\item Approximately 300,000 speakers
			\item Agglutinative morphology
			\item Very little work on computational tools
		\end{itemize}
	}

	\headerbox{Morphological Transducers}{name=morphtrans,below=tyvan}{
		\htwo{Morphological transducers}
		\begin{itemize}
			\item Efficient (in speed \& size) models of a language's morphology
			\item Take a surface form, and produce valid lexical form(s)
			\item Take a lexical form, and produce valid surface form(s)\vspace{-0.1ex}\\
		%\end{itemize}
		%\scalebox{0.98}{
			алдым\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{ал\tag{v}\tag{tv}\tag{ifi}\tag{p1}\tag{sg}},~~\texttt{алд\tag{n}\tag{px1sg}\tag{nom}}\\
			өөнде\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{өг\tag{n}\tag{px3sp}\tag{loc}}
		%}
		\end{itemize}
		\dividerspace{}

@@

		\htwo{Approach}
		\begin{itemize}
			\item two-level method \parencite{koskenniemi83}
			\item \textbf{morphotactics} implemented in \texttt{lexc}
			\item \textbf{morphophonology} implemented in \texttt{twol} (SPE-style rules)
			\item compiled separately; compose-intersected to single transducer\vspace{-0.1ex}\\
			алдым\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{ал\hilitegrey{>}\archiphon{D}\archiphon{I}\hilitegrey{>}м}\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{ал\tag{v}\tag{tv}\tag{ifi}\tag{p1}\tag{sg}}\vspace{-0.1ex}\\
			алдым\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{алд\hilitegrey{>}\archiphon{I}м}\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{алд\tag{n}\tag{px1sg}\tag{nom}}\\
			өөнде\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{өг\hilitegrey{>}\archiphon{z}\archiphon{I}\archiphon{n}\hilitegrey{>}\archiphon{D}\archiphon{A}}\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{өг\tag{n}\tag{px3sp}\tag{loc}}
		\end{itemize}

@@

		\headerbox{Development cycle}{name=development,below=harglebargle,span=1}{
		\centering
		\begin{tikzpicture}[xscale=1.45,yscale=2.212]%, auto]

>>>>

	\headerbox{Tuvan}{name=tyvan,column=0,row=0}{
		\includegraphics[width=\textwidth]{img/tuvanmap}
		\tikzoverlay[text width=1in] at (2.5in, -0in) {
			\includegraphics[width=1in]{img/Flag_of_Tuva}
		};
		\vspace{-1.2em}
		\begin{itemize}
			\item Sayan Turkic language
			\item Spoken in Tuva Republic and nearby
			\item Approximately 300,000 speakers
			\item Agglutinative morphology
			\item Very little work on computational tools
		\end{itemize}
	}

	\headerbox{Morphological Transducers}{name=morphtrans,below=tyvan}{
		\htwo{Morphological transducers}
		\begin{itemize}
			\item Computational models of a language's morphology
			\item Efficient in speed \& size
			\item Take a surface form, and produce valid lexical form(s)
			\item Take a lexical form, and produce valid surface form(s)%\vspace{-0.1ex}\\
		\end{itemize}
		%\scalebox{0.98}{
			алдым\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{ал\tag{v}\tag{tv}\tag{ifi}\tag{p1}\tag{sg}},~~\texttt{алд\tag{n}\tag{px1sg}\tag{nom}}\\
			өөнде\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{өг\tag{n}\tag{px3sp}\tag{loc}}
		%}
		%\end{itemize}
		\dividerspace{}

@@

		\htwo{Approach}
		\begin{itemize}
			\item two-level method \parencite{koskenniemi83}
			\item \textbf{morphotactics} implemented in \texttt{lexc}
			\item \textbf{morphophonology} implemented in \texttt{twol}
			\item compiled separately; compose-intersected to single transducer%\vspace{-0.1ex}\\
		\end{itemize}
			алдым\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{ал\hilitegrey{>}\archiphon{D}\archiphon{I}\hilitegrey{>}м}\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{ал\tag{v}\tag{tv}\tag{ifi}\tag{p1}\tag{sg}}\vspace{-0.1ex}\\
			алдым\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{алд\hilitegrey{>}\archiphon{I}м}\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{алд\tag{n}\tag{px1sg}\tag{nom}}\\
			өөнде\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{өг\hilitegrey{>}\archiphon{z}\archiphon{I}\archiphon{n}\hilitegrey{>}\archiphon{D}\archiphon{A}}\hfill{}{\qipa \hilitetwo{↔}}\hfill{}\texttt{өг\tag{n}\tag{px3sp}\tag{loc}}
		%\end{itemize}
		\begin{itemize}
			\item mostly hand-written; some parts automatable
		\end{itemize}

@@

		\headerbox{Development cycle}{name=development,below=harglebargle,span=1}{
		\centering
		\begin{tikzpicture}[xscale=1.45,yscale=2.19]%, auto]
